### 2016-06-19 appendix.tex
Except experiments
dan teng

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}
\begin{proof}
If $P$ is a valid pattern in original trajectories, 
let $s$ be the object with smallest ID in $P.O$. 
Based on the definition of GCMP, $\forall t \in P.T$, $\forall o \in P.O$, $C_t(s) = C_t(o)$.
It follows that all object $o \in P.O$ are in $Sr_s$. 
Furthermore, every timestamp in $P.T$ is included
in $Sr_s$. Therefore, $P$ is a valid pattern in $Sr_s$. This completes the proof of Theorem~\ref{THM:SPM_CORRECT}.
The correctness of Lemma~\ref{LEM:SPM_CORRECT} can be directly derived from the above arguments:
let $o_i$ be the smallest element in $p_i.O$ and $o_j$ be the smallest element in $p_j.O$. 
Since $p_i$ and $p_j$ belongs to different stars, then $o_i \neq o_j$, 
therefore $p_i.O \not\equiv p_j.O$. This proves the lemma.
\end{proof}

\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
\begin{proof}
Let $\mathbb{A}^*$ be the optimal numbering wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be an entry in the adjacent matrix of $G$. Note that edges in $G$ are independent. 
Let $d_i$ denote the degree of vertex $i$ in $G$. 
It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the vertex
with smaller IDs, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, 
is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) 
						&\leq \exp(\frac{-2t^2}{n}) \\
						&= \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

\subsection{Proof of Theorem~\ref{THM:SPM_TM}}
\begin{proof}
Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
by proof of contradiction, any subset of $P_1.T$ cannot
be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
\end{proof}

>>>>

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}

\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
\begin{proof}
Let $B*$ be the assignment matrix wrt the optimal numbering.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
let $d_i$ denote the degree of vertex $i$, 
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
vertexes does not affect the average degree.
Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

By definition, $c_i = \Sigma_{1\leq j \leq n} b_{i,j}$, 
is a sum of $n$ independent 0-1 variables. Taking expectation on both sides, 
we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} b_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$.
 Let $\mu =E[c_i] = d/2$, 
$t = \sqrt{n\log n}$, by Hoeffding's Inequality, the following holds:
\begin{equation*}
\begin{split}
	Pr(c_i \geq \mu + t) 
						&\leq \exp(\frac{-2t^2}{n}) \\
						&= \exp(-2\log n) = n^{-2}
\end{split}
\end{equation*}

The first step is due to the fact that all $b_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute back $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(\Gamma-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. 
With the fact that $\Gamma^* \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $\Gamma$ and $\Gamma^*$ is less than $O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$), we may use
the Chernoff Bound instead of Hoeffding's Inequality to derive a tighter bound of 
$O(\sqrt{\log n}) $ with the similar reasoning.
\end{proof}

%\subsection{Proof of Theorem~\ref{THM:SPM_TM}}
%\begin{proof}
%Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
%Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
%by proof of contradiction, any subset of $P_1.T$ cannot
%be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
%In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
%\end{proof}

### 2016-06-19 sec1_introduction.tex
Need to update \eta
Need to describe \eta
Except experiments
dan teng

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori method is adopted to mine the co-movement patterns. Third, we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

%
%Second, we investigate on deploying our GCMP detector to facilitate scalable pattern mining.
%In order to support large real trajectories, to the best of our knowledge, we
%are the first to study GCMP mining in MapReduce (MR) systems. There are a
%few challengers associated with designing an efficient MR-based pattern 
%detection algorithms. 
%
%First, in order to support effective parallelism, we need
%to partition the trajectory database with almost equal sizes. Our initial attempts
%develops a temporal based partition approached named as 
%\emph{Temporal Replication and Mining} (TRM). In TRM, neighboring snapshots form
%a equal-sized partition such that co-movement patterns can be mined independently.
%However, such a scheme require $O(|\mathbb{T}|)$ replication of input, which is 
%inefficient for large-scale trajectories. To support efficient mining, 
%we design a novel \emph{Star Partition and Mining} (SPM) approach which utilize
%the potential co-movement relationship among objects.
%
%Our initial attempt develops a naive but effective 
%\emph{Temporal Replication and Mining} (TRM) approach 
%which requires to replicate entire data set $O(|\mathbb{T}|)$ times. Such a 
%large set of

%There
%are a few challenges arises in designing the MR based pattern detection algorithm.
%First, we

%The major challenge
%we face is to make proper data partitions such
%that each partition can be efficiently processed independently. Our initial attempt develops
%a naive but effective \emph{Temporal Replication and Mining} (TRM) approach which requires to replicate
%entire data set $O(|\mathbb{T}|)$ times. To improve the efficiency, we design a novel \emph{Star Partition and Mining} (SPM)
%algorithm. In SPM, potential co-moving objects are first grouped into partitions. Subsequently,
%an apriori based method is applied to discover the patterns from each partition.
%Despite the simpleness of the star partition, we theoretically prove its correctness
%and optimality. Using SPM as the foundation, we develop and integrate
%a series of optimization techniques including \emph{edge simplification}, \emph{candidate pruning}
%and \emph{forward closure checking} to further boost the
%performances.
%

%
%Second, we investigate how to deploy our GCMP detector  on Spark for scalable pattern mining.
%The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
%In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
%of the partitions. Such properties ensure that neither false-patterns 
%nor miss-patterns are possible in our solution. To meet such partition requirements
%as well as to keep the shuffle amount to a minimum, 
%we first design a naive \emph{Temporal Replication and Mining} (TRM)
%approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
%method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
%Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
%as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
%a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
%GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$. 
%Despite the simpleness of star partition, we theoretically prove its optimality.
%Furthermore, we utilize \emph{temporal monotonicity} to further reduce the 
%shuffling and mining cost in SPM. 
%Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
%Apache Spark which is one of the most popular MapReduce platforms.

%we design a novel star-based partition scheme to efficiently partition objects based on their
%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

We conduct a set of extensive experiments on XXX datasets with billion-scale trajectory points. The results show that XXX.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a naive \emph{temporal replication and mining} solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:opt} discusses various optimization techniques. Section~\ref{sec:exp} conducts extensive experiments to verify the usefulness and efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

>>>>

Second, we investigate deploying our GCMP detector on MapReduce platforms (such as Hadoop and Spark) to tackle the scalability issue. Our technical contributions are three-fold. First, we replicate the snapshots in multiple data chunks to support efficient parallel processing. Second, we devise a novel \emph{Star Partition and Mining} (SPM) algorithm as a fine-granularity partitioning strategy to achieve workload balance. For each star, an Apriori method is adopted to mine the co-movement patterns. Third, we leverage the \emph{temporal monotonicity} property of GCMP to design several optimization techniques including \emph{edge-simplification} to prune initial candidates, \emph{temporal apriori pruning} and \emph{forward closure checking} to reduce the number of enumerated candidates in the Apriori algorithm.
%
%we propose two types of optimization techniques to further improve the performance, including \emph{edge-simplification} to boost the shuffle process and \emph{temporal monotonicity pruning} and 
%\emph{forward closure checking} to significantly reduce the number of enumerated candidates in the Aproiro algorithm.

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
our scheme runs within 10 minutes using 135 cores. Whereas centralized solution takes near 7 hours for 
1 million trajectory points.
Moreover, our optimized SPM methods achieves upto XXX times efficiency
as compared to the baseline algorithm with near linear scalability.

The rest of our paper is organized as follows: Section~\ref{sec:related_works} summarizes the relevant literature on 
trajectory pattern mining. Section~\ref{sec:definition} states the problem definition of our general co-movement pattern mining. Section~\ref{sec:trm} provides a baseline solution. An advanced solution named
\emph{star partition and mining} is presented in Section~\ref{sec:spm}. Section~\ref{sec:opt} discusses various optimization techniques. Section~\ref{sec:exp} conducts extensive experiments to verify the efficiency of our system. Finally Section~\ref{sec:concl} concludes the paper.

### 2016-06-19 sec5_spm-bk.tex
Except experiments
dan teng

\subsubsection{Optimal Star Partition}
An important concern in design parallel algorithms is 
the distribution of work loads.  
Traditionally, the quality of a partition strategy 
is measured based on two aspects: (1) the number of result partition, which
affects the maximum parallelism
(2) the size balance of partitions, which affects the finishing
time of a job. Unlike TRM where each partition
contains equal-sized snapshots, the size distribution 
of stars in SPM remains unknown.
Nevertheless, we notice that, in SPM, the total sizes of 
stars are invariant. Therefore, the quality of a star partition
can be formalized as the \emph{skewness}, which is the maximum star size
among all stars. Smaller \emph{skewness} naturally results in more partitions
and less imbalance.

@@

Interestingly, we note that the \emph{skewness} of star partition is affected by
the way the vertexes are numbered in the connection graph. For example,
Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
of the same connection graph, but produces two different set of stars. 
The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
Apparently the upper partitioning is inferior because its \emph{skewness} is 5 while the
lower one's \emph{skewness} is 3.

Ideally we wish to find a numbering scheme of connection graph
that minimize the \emph{skewness}.
To quantify, we use an linear algebra model as follows: 
Let $G$ denote a connection graph.
Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
Let $(A:a_{i,j})$ be a boolean assignment matrix wrt. $\mathbb{A}$
(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$). 
Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
vector. Let $\vec{c} = A\vec{b}$, then each $c_i \in \vec{c}$ 
denotes the size of the star $Sr_i$.
Therefore, minimizing the \emph{skewness} can be formulated as follows:
\begin{equation}
\mathbb{A}  = \argmin(||A\vec{b}||_\infty) \text{,where } ||A\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

It is challenging to directly optimize the above equation. 
First, suppose there are $n$ vertexes in $G$, enumerating
all possible $\mathbb{A}$s leads to $n!$ combinations. 
Such a high complexity is trivially unpractical. Second,
since $G$ is only conceptual at runtime, 
the load planning cannot be done beforehand. 
Despite these challenges, we observe that there is a 
$O(1)$ time solution which is good enough as stated in the 
following theorem.

\begin{theorem}[Balance of Star Partition]
\label{THM:SPM_LB}
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For an random numbering, $\mathbb{A}$, with high probability, the 
absolute skewness difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is with probability $1-1/n$, 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
equation holds:
\begin{equation*}
Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
\end{equation*}

Utilizing Theorem 3, in SPM, it is safe to choose the object IDs as 
the vertex number. This because in reality, object IDs are often 
hashed and can be deemed as random.

>>>>

\subsubsection{Optimal Star Partition}
An important concern in designing a partition 
algorithm is the skewed execution times for
each partition. If there are partitions
taking significant long time to execute, they would become
the bottleneck of the entire system. Such long time-taken partitions
are referred as \emph{stragglers}~\cite{kwon2012skewtune,xin2013shark,coppa2015data}. In TRPM, where
each partition contains a equal-sized snapshots, the \emph{straggler}
is not a concern. However, in SPM, the size distribution of
stars remains unknown. It is necessary to analyze the 
distribution of SPM workloads. We use $\Gamma$ to indicate
the size of \emph{straggler} in star partition. Intuitively,
a large $\Gamma$ means the system has a more prominent bottleneck. 
And smaller $\Gamma$ is always preferred.

% As we shown in Algorithm~\ref{algo:apriori_mining},
%the running time of a star partition is correlated with the number of edges.
%Therefore, we use the number of edges to measure the \emph{straggler}, where
%the \emph{straggler} refers to the largest star. W.L.O.G, we use $\Gamma$ to
%denote the size of the \emph{straggler}. Intuitively, a large $\Gamma$ indicates
%a large straggler

%
%We use the conventional indicator \emph{straggler} to analyze the distribution of SPM, where 
%the \emph{straggler} is determined by the largest size of stars 
%in the SPM. Intuitively, a large \emph{straggler}

%An important concern in design 
%the distribution of work loads. 
%Traditionally, the quality of a partition strategy 
%is measured based on two aspects: (1) the number of result partition, which
%affects the maximum parallelism
%(2) the size balance of partitions, which affects the finishing
%time of a job. 
%
%Unlike TRM where each partition
%contains equal-sized snapshots, the size distribution 
%of stars in SPM remains unknown. To formally analyze
%the distribution of SPM workloads, we use the concept 
%of \emph{strangler}

%Nevertheless, we notice that, in SPM, the total sizes of 
%stars are invariant. Therefore, the quality of a star partition
%can be formalized as the \emph{skewness}, which is the maximum star size
%among all stars. Smaller \emph{skewness} naturally results in more partitions
%and less imbalance.

@@

Interestingly, we note that the size of \emph{straggler} (i.e., $\Gamma$) 
of star partition is affected by
the way the vertexes are numbered in the aggregate graph. For example,
Figure~\ref{fig:star-alt} gives two valid numbering of vertexes 
of the same aggregate graph, but produces two different set of stars. 
The upper partitioning constructs 4 stars with the maximum star consisting of 5 edges.
The lower partitioning constructs 5 stars with the maximum star consisting of 3 edges.
Apparently the upper partitioning is inferior because its $\Gamma$ is 5 while the
lower one's $\Gamma$ is 3.

Ideally we wish to find a numbering scheme of aggregate graph
that minimize the size of straggler, (i.e, $\Gamma$).
To quantify, we use an linear algebra model as follows: 
Let $G$ be an aggregate graph, with a $n \times n$ adjacent matrix $A$.
A numbering scheme is in fact a permutation of $A$. Therefore,
the adjacent matrix of a numbered graph can be represented as $PAP^T$
where $P \in \mathbb{P}$ is a 
\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
Since in SPM we assign each edge $e(i,j)$ to the lower vertex, 
then the matrix $B=\text{triu}(PAP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
%Let $P \in \mathbb{P}$ be a \emph{permutation matrix} with dimension $n$.
%Then numbering with $P$ generates an adjacent matrix $B = PAP^T$.
%Let $\mathbb{A}$ be
%the set of all numbering schemes. A numbering scheme
%$A \in \mathbb{A}$ is a boolean assignment matrix 
%(i.e., $a_{i,j} \in A $ indicates whether vertex $j$ is included in $Sr_i$. Apparently, $a_{i,j} \neq a_{j,i}$).
%%Let $\mathbb{A}$ be an arbitrary numbering of vertexes in $G$.
%Given a numbering scheme, let $(A:a_{i,j})$ be a boolean assignment matrix
%(i.e., $a_{i,j}$ indicates whether vertex $j$ is included in $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector. Let $\vec{c} = B\vec{b}$, then each $c_i \in \vec{c}$ 
denotes the size of the star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. The minimum size of straggle, $\Gamma^*$
can then be formulated as follows:
\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

It is challenging to directly optimize the above equation. 
First, suppose there are $n!$ permutation matrices. 
Such a high complexity is trivially unpractical. Second,
since $G$ is unknown in prior,
the load planning cannot be done beforehand. 
Despite these challenges, we observe that there is a 
$O(1)$ time solution which is good enough as stated in the 
following theorem.

\begin{theorem}[Balance of Star Partition]
\label{THM:SPM_LB}
Let $G$ be an aggregated graph with $n$ vertexes and the average degree $d$.
Let $\Gamma^*$ be optimal size of straggler.
Let $\Gamma$ be the size of straggler wrt an random numbering $P$. 
With high probability, the difference between $\Gamma$ and $\Gamma^*$ is $O(\sqrt{n \log n})$.
That is,  with probability $1-1/n$, 
$\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}

In fact, we have a tighter bound of $\Gamma - \Gamma^*$ if 
the aggregate graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, with
high probability, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
Utilizing Theorem~\label{THM:SPM_LB}, in SPM, it is safe to choose the object IDs as 
the vertex number. This because in reality, object IDs are often 
hashed and can be deemed as random.
